Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with \pkg{ACSNMineR} and \pkg{RNaviCell} packages

### 2016-09-01 jss/Deveau.tex
[skip ci] minor change in text

The \code{enrichment} function can take up to eight arguments: the gene list (as
a character vector), the list of maps that will be used to calculate enrichment
or depletion, the type of statistical test (either the Fisher exact test or the
hypergeometric test), the module minimal size for which the calculations will be
done, the universe, the p-value threshold and the alternative ("greater" for
calculating over-representation, "less" for depletion and "both" for both
tests).

>>>>

The \code{enrichment} function can take up to nine arguments: the gene list (as
a character vector), the list of maps that will be used to calculate enrichment
or depletion, the type of statistical test (either the Fisher exact test or the
hypergeometric test), the module minimal size for which the calculations will
be done, the universe, the p-value threshold, the alternative hypothesis
("greater" for calculating over-representation, "less" for depletion and "both"
for both tests) and a list of genes that should be removed from the universe
(option "Remove\_from\_universe"). This option may be useful for instance if we
know beforehand that a number of genes are not expressed in the samples
considered.
